\PYGEOMETRY{}: a Python library for the creation of Monte Carlo radiation transport physical geometries

### 2020-09-16 public/paper/pyg4ometry.tex
"kept a similar" isn't english
Registry -> Registry instance

The core of \PYGEOMETRY{} consists of Python classes that mimic Geant4 solids, logical volumes, physical volumes, GDML parameters and material classes.
The constructors of the Python classes are kept as close to the original Geant4 C++ implementation as possible so that \PYGEOMETRY{} users do not have to learn 
a new API. For example the \verb|G4Box| class in Geant4, has the XML tag \verb|Box| in GDML and is represented by the \pyinline{Box} 
class in \PYGEOMETRY{}. The Python object initialiser is kept a similar to the Geant4 C++ constructor, but the length definitions are those used by GDML. For example, 
GDML uses full lengths whilst Geant4 uses half lengths. Geometry construction in Python proceeds in a way which is very similar to geometry construction in Geant4. 
A user relatively familiar with Geant4 should be able to start creating geometry in \PYGEOMETRY{} immediately. In the following sections novel or important developments 
in \PYGEOMETRY{} are described.

@@

%%%%%%%%%%%%%%%%%  Input and output  
For each input format available in \PYGEOMETRY{}  (GDML, STL, FLUKA and STEP) a dedicated \emph{Reader} class is implemented, so \verb|gdml.Reader|,
\verb|stl.Reader|, \verb|fluka.Reader| and \verb|freecad.Reader|. Each reader constructs the appropriate Geant4 classes and provides a \verb|Registry| which 
can be used or manipulated by the user. 
Output consists of taking the registry and writing the appropriate GDML.

>>>>

The core of \PYGEOMETRY{} consists of Python classes that mimic Geant4 solids, logical volumes, physical volumes, GDML parameters and material classes.
The constructors of the Python classes are kept as close to the original Geant4 C++ implementation as possible so that \PYGEOMETRY{} users do not have to learn 
a new API. For example the \verb|G4Box| class in Geant4, has the XML tag \verb|Box| in GDML and is represented by the \pyinline{Box} 
class in \PYGEOMETRY{}. The Python object initialiser is very similar to the Geant4 C++ constructor, but the length definitions are those used by GDML. For example, 
GDML uses full lengths whilst Geant4 uses half lengths. Geometry construction in Python proceeds in a way which is very similar to geometry construction in Geant4. 
A user relatively familiar with Geant4 should be able to start creating geometry in \PYGEOMETRY{} immediately. In the following sections novel or important developments 
in \PYGEOMETRY{} are described.

@@

%%%%%%%%%%%%%%%%%  Input and output  
For each input format available in \PYGEOMETRY{}  (GDML, STL, FLUKA and STEP) a dedicated \emph{Reader} class is implemented, so \verb|gdml.Reader|,
\verb|stl.Reader|, \verb|fluka.Reader| and \verb|freecad.Reader|. Each reader constructs the appropriate Geant4 classes and provides a \verb|Registry| instance which 
can be used or manipulated by the user. 
Output consists of taking the registry and writing the appropriate GDML.
